Wavelet Spatio-Temporal Change Detection on multi-temporal SAR images

### 2021-12-20 tex/RebutalLetter/RebutalLetter.tex
ajustes++ (20dez21)

\medskip
%-------------------------------------
\begin{mybox}{Comment 1}
\textit{Data used: In the entire paper there is no mention of the type of data used. Are this Sentinel-1 GRD images?
\textcolor{red}{Also please consider acknowledging ESA for the use of data.}}

\medskip
\textbf{R:} The data was obatined from the SAR sensor onboard the Sentinel-1 satellite.
\textcolor{green}{Verdade... vamos citar a fonte, apenas foi dito o sensor.}
\end{mybox}
%-------------------------------------

@@

\medskip
%-------------------------------------
\begin{mybox}{Comment 5}
\textit{Real data info and preprocessing: There is absolutely no information about what satellite data are used. I
assume this are Sentinel-1 GRD, but please provide info on that. Also there is no info on what pre-processing
you use. \textcolor{red}{Did you do calibration, terrain correction, noise removal, geocoding?}}

\medskip
\textbf{R:} We included more detailed information about the images used in the real data application. They are indeed Sentinel-1 images.

\textcolor{green}{Não houve pre-processamento, mas é interessante incluir isso no texto. Eu farei isso.}
\end{mybox}
%-------------------------------------

>>>>

\medskip
%-------------------------------------
\begin{mybox}{Comment 1}
\textit{Data used: In the entire paper there is no mention of the type of data used. Are this Sentinel-1 GRD images? Also please consider acknowledging ESA for the use of data.}

\medskip
\textbf{R:} The reviewer is correct, the Sentinel-1 GRD images were employed in this research. The revised text includes a description of this sensor/dataset. Acknowledgments to ESA were also included at the end of the manuscript. Thank you.
\end{mybox}
%-------------------------------------

@@

\medskip
%-------------------------------------
\begin{mybox}{Comment 5}
\textit{Real data info and preprocessing: There is absolutely no information about what satellite data are used. I
assume this are Sentinel-1 GRD, but please provide info on that. Also there is no info on what pre-processing
you use. Did you do calibration, terrain correction, noise removal, geocoding?}

\medskip
\textbf{R:} As mentioned (in comment \#1), we added more details about the adopted images in the experiment with actual remote sensing data.

% used in the real data application. They are indeed Sentinel-1 images.

%\textcolor{green}{Não houve pre-processamento, mas é interessante incluir isso no texto. Eu farei isso.}
\end{mybox}
%-------------------------------------

### 2021-12-20 tex/paper.wecs/wecs_tgrs.tex
ajustes++ (20dez21)

Each image contains the amplitude signal backscatters relative to VV and VH polarizations, a spatial resolution of \SI{10}{\meter} and support of $1538 \times 1556$ pixels wide.
Figures~\ref{figImgSentinel2015} and \ref{figImgSentinel2017} depict the first and last images of the time series, where it is possible to compare and identify some landscape changes.

@@

% use section* for acknowledgment
%\section*{Acknowledgment}

>>>>

Each image contains the amplitude signal backscatters relative to VV and VH polarizations, a spatial resolution of \SI{10}{\meter} and a support of $1538 \times 1556$ pixels wide in ground range projection. 
Specifically, these images where obtained from the \textit{Sentinel-1 SAR GRD} dataset maintained by the European Space Agency \cite{ESA2021}.
%
Figures~\ref{figImgSentinel2015} and \ref{figImgSentinel2017} depict the first and last images of the time series, where it is possible to compare and identify some landscape changes.

@@

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank the European Space Agency (ESA) for providing the Sentinel-1 data used in this research.
